`r title`

### 2017-12-07 lib/report.Rmd
updating
progress

---
params:
  state: ""
  city: ""
title: "`r paste(params$city, params$state, sep = ', ')`"
---

@@

\begin{center}
`r prettyNum(total_rows, big.mark = ",")` rows

`r date_range[1]` to `r date_range[2]`
\end{center}

@@

Top 20 reasons for stop cumulative percentage: `r reason_for_stop_top_20_pct`

@@

>>>>

---
params:
  state: ""
  city: ""
---

@@

---
title: `r title`
---

\begin{center}
2010 Census population: `r comma_num(population)`

`r comma_num(total_rows)` rows from `r date_range[1]` to `r date_range[2]`
\end{center}

@@

@@

\newpage

\begin{center}
\textbf{Metadata}
\end{center}

```{r loading_problems_count_table}
loading_problems_count_table
```

```{r loading_problems_random_sample_sorted_table}
loading_problems_random_sample_sorted_table
```

\newpage
```{r missing_columns_added_table}
missing_columns_added_table
```

```{r enforce_types_table}
enforce_types_table
```

```{r sanitize_table}
sanitize_table
```
